Global Distribution of Unintended Pregnancies and Contraceptive Usage

### 2024-04-16 products/manuscript/Manuscript.qmd
Figure Labels
Fixed all figure labels to make sure they render correctly now.

We created a multitude of exploratory plots to understand our data better. The first exploratory result shown in @fig-1 displays the distribution of the outcome variable: percent of unintended pregnancies due to short acting reversible methods. The `pct_upreg_sarc` variable is slightly skewed to the right with an average around 12%.
```{r}
#| message: false
#| label: fig-1
#| fig-cap: "Plot 1: Histogram Depicting Number of Countries With Percent Unintended Pregnancy Using SARC"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "exploratory-figures", "pctupreg_sarc_distribution.png"))
```

The next set of variables we explored were the total counts of women using each birth control method. There were two large outliers that prevented the graphs from being useful. After exploring the outliers, we standardized using the population size of reproductive aged women (15-49 years). There is a positive association between the percentage of unintended pregnancies among short acting reversible method users and the total number of women using that method of birth control, which is to be expected. Our outcome variable is the number of unintended pregnancies among women who are using short-acting reversible contraception, so the number of unintended pregnancies that can be classified in this outcome is dependent on the number of women using this type of contraception. This percentage should increase as the number of women using short acting-reversible contraception increases because more women are at risk of experiencing an unintended pregnancy due to this contraception if they are using this type of contraception in the first place. This outcome variable does not speak to the effectiveness of short-acting reversible contraception, so it makes sense that our outcome would increase as more women put themselves at risk of experiencing the outcome through becoming classified as short-acting reversible contraception users. As explained in the supplementary material, the dataset includes the percentage of unintended pregnancies among long-acting reversible contraception and sterilization users, traditional birth control users, and users who do not use a method of birth control. Each of these percentages are positively associated with number of people in its respective classification group that it represents. The association for the contraception that we chose to focus on for this analysis, short acting reversible contraception, is displayed in @figure2.
```{r}
#| message: false
#| label: figure2
#| fig-cap: "Figure 1: Graph Depciting Percent Unintended Pregnancy by Standarized Count of Total Women"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "exploratory-figures", "pctupreg_totalsarc.png"))
```

We stratified these four graphs by region to examine how the relationship differs across each of the regions which is shown in @figure3 . The graph for short acting reversible methods shows clearer differences between regions, and Latin America/the Caribbean leads in the percentage of unintended pregnancies in this category, but Africa shows the sharpest increase in percentage of unintended pregnancies as the total population increases.
```{r}
#| message: false
#| label: figure3
#| fig-cap: "Figure 2: Graph Depicting Percent Unintended Pregnancies Using SARC by region"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "exploratory-figures", "pctupreg_sarc_stratified.png"))
```

We also created violin plots using the categorical usage variables for each birth control method as shown in @figure4. It appears that the distribution of short acting reversible method usage is skewed towards lower percentages of unintended pregnancies across all usage levels, suggesting that more countries have lower percentage of unintended pregnancies among women using this method. The high usage countries appear to have a bottleneck in percentage of unintended pregnancies. The high and low usage countries appear to be skewed towards higher levels of unintended pregnancies, but the medium usage countries appear to have lower percentage of unintended pregnancies. 
```{r}
#| message: false
#| label: figure4
#| fig-cap: "Plot 5: Violin Plot Depicitng Usage of SARc Per Region"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "exploratory-figures", "sarc_pctupreg_violin.png"))
```

Lastly, we explored the predictor variables that will be used in our models, and the graphs are shown in @figure5 - @figure10. The Africa region accounts for most of the observations with about 53 countries, followed by Asia that includes about 35 countries. Latin America/the Caribbean accounts for about 25 countries. Europe and Oceania account for the least number of observations. The distribution of women currently married is approximately normal with an average around 57% and no major outliers. The distribution of women never married is slightly skewed to the right with an average around 30%, but there are a few outliers greater than 60%. The distribution of the total maternal mortality rate is highly skewed to the right with a couple outliers. We would have expected the highest rates to belong to India and China because they have the most people, but it is Chad, Sierra Leone, and South Sudan that account for the highest rates of total maternal mortality, which each belong to the African region. The distribution of the maternal mortality rate from unintended pregnancies is highly skewed to the right with a couple outliers, which is to be expected based on the trend shown in the previous histogram. Chad and South Sudan also account for the highest rates of maternal mortality in this category. The distribution of maternal mortality rate from abortions is also highly skewed to the right. The outliers are accounted for by Gambia and Mauritania in this predictor, which both belong to the African region.
```{r}
#| message: false
#| label: figure5-figure10
#| fig-cap: "Predictor Variable Distributions"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "exploratory-figures", "region_distribution.png"))
knitr::include_graphics(here("results", "figures", "exploratory-figures", "currmarried_distribution.png"))
knitr::include_graphics(here("results", "figures", "exploratory-figures", "nevmarried_distribution.png"))
knitr::include_graphics(here("results", "figures", "exploratory-figures", "matdeaths_distribution.png"))
knitr::include_graphics(here("results", "figures", "exploratory-figures", "matdeathsupreg_distribution.png"))
knitr::include_graphics(here("results", "figures", "exploratory-figures", "matdeathsabs_distribution.png"))

@@

## Basic statistical analysis
We completed a simple linear regression analysis with each of the 7 predictors shown in @table2. The predictor with the strongest positive relationship with the outcome is total number of women using short acting reversible methods (`sarc_standard`). This percentage should increase as the number of women using short acting-reversible contraception increases because more women are at risk of experiencing an unintended pregnancy due to this contraception if they are using this type of contraception in the first place.

```{r}
#| message: false
#| label: table2
#| fig-cap: "Table 2: Strongest Predictor: sarc_standard"
#| echo: FALSE
readRDS(here("results","tables", "resulttable1.rds")) 
```

The second model we created used the region predictor, which revealed that the Latin America/the Caribbean region had the strongest relationship with the outcome variable followed closely by the Asia region. The Oceania region does not appear to have a strong effect on the outcome variable with the Europe region only showing a slightly larger association. These associations can be seen in @table3.
```{r}
#| message: false
#| label: table3
#| fig-cap: "Table 3: Regional Predictor"
#| echo: FALSE
readRDS(here("results","tables", "resulttable2.rds")) 
```
Details about the 9 different models we created can be found in the statistical-analysis.qmd file in the code > analysis-code folder along with an exploration of the correlation between predictors.

@@

We created one model with all 5 predictors using multiple linear regression, shown in @table4. This model shows the strongest predictor is the number of women using short acting reversible contraception. The next strongest predictor is the European region followed by the Latin America/the Caribbean region and the Asia region, which is a shift from the model with the singular region predictor. The Oceania region now has a negative association with the outcome. The currently married predictor is associated with a weak decrease in the outcome. The coefficient estimates for the rate of maternal death due to unintended pregnancies and abortion both show a very weak positive association with the outcome. 
```{r}
#| message: false
#| label: table4
#| fig-cap: "Table 4: Multiple Linear Regression with 5 Predictors"
#| echo: FALSE
readRDS(here("results","tables", "resulttable8.rds")) 
```
To determine which model performed the best, we started by examining the RMSE and MAE performance metrics. We found that the model with the standardized total count of women using the short acting reversible contraception method performed the best in a single predictor model compared to the percent of currently married women and the rate of maternal mortality due to abortion. @table5 shows the RMSE and MAE values for each of these three models compared to the null model with no predictors. The model with the population size using SARCs is the only single predictor model that performs better than the null. The full model with all 5 predictors performs the best with the lowest RMSE and MAE values. 
```{r}
#| message: false
#| label: table5
#| fig-cap: "Table 5: Performance Metric Comparisons"
#| echo: FALSE
readRDS(here("results","tables", "resulttable14.rds")) 
```
We used cross-validation of the two best models to determine how well the model performs on data it has not seen yet by splitting the data into testing and training pieces. The cross-validated results, shown in @table6 lead to the same conclusion: the multiple linear regression model with 5 predictors performs better. The RMSE value for the single predictor model with `sarc_standard` is 4.822226, which is lower the the first RMSE value of 5.143319. While the RMSE value for the multiple linear regression model is slightly higher than the first time it was calculated, it is still lower than the single predictor model. Additionally, the standard error of the RMSE for the multiple linear regression model is 0.2768, which is lower than the standard error of the RMSE for the single predictor model of 0.3528. This means there is higher variance in the single predictor model. The R-squared value of 0.8206 for the multiple linear regression model is higher than 0.7861 for the single predictor model, which means the multiple linear regression model accounts for more of the variability in the data. Overall, the multiple linear regression model performs better.
```{r}
#| message: false
#| label: table6
#| fig-cap: "Table 6: Cross Validation Performance Metric Comparisons"
#| echo: FALSE
readRDS(here("results","tables", "resulttable15.rds")) 
```

Since we determined that the full model with all 5 predictors performs best, we graphed the predicted versus observed values using this model with both the testing and training data to further examine model performance. As seen in @figure11, the training model predictions, shown in teal, hover pretty closely around the expected relationship between the outcome and the 5 predictors, which is depicted as the 45 degree line. The testing model predictions, shown in coral, are much more extreme than the training model predictions because they are farther from the 45 degree line. While there is some overlap between the two sets of predictions, it is likely that our model is overfitting the data. 
```{r}
#| message: false
#| label: figure11
#| fig-cap: "Figure 3: Evaluating Final Model Performance on Test Data"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "final-figures", "fullmodelpred.png"))
```
We went one step further to examine the uncertainty in the full model predictions using the bootstrap method with 100 resamples of the training data. The figure shown in @figure12 displays the 95% confidence intervals, shown as dark blue lines, for the predictions made by the model. The confidence intervals are narrow, which shows there is minimal uncertainty in the model prediction. For the predictions that do not fall on the expected 45 degree line, the confidence intervals do not intersect with the line either. These findings increase the validity of the conclusion that the model is overfitting the data because there is not much uncertainty in the predictions. 
```{r}
#| message: false
#| label: figure12
#| fig-cap: "Figure 4: Evaluation of Uncertainty in Full Model Predictions"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "final-figures", "bootstrappred.png"))
```

Since we have evidence that our model overfits the data, the last technique we want to use to explore our full model is Lasso regression. This technique could reveal predictors that should not be included in our final model, which could reduce the risk of overfitting. As seen in @table7, the LASSO regression coefficients are much smaller than the first full model we created without the regularization penalty, but all 5 predictors remain in the model. The `sarc_standard` predictor still has the strongest relationship with the outcome. The percent of women currently married, rate of maternal deaths due to unintended pregnancies, and rate of maternal deaths to due to abortion all have weak negative associations with the outcome. This process confirms that our final model should contain all 5 predictors. 
```{r}
#| message: false
#| label: table7
#| fig-cap: "Table 7: LASSO Regression Results"
#| echo: FALSE
readRDS(here("results","tables", "resulttable16.rds")) 
```
It is important to tune the hyperparameters associated with LASSO regression to determine the model that fits best, which is shown in @figure13. As the regularization penalty increases past 1, we see that the RMSE value increases exponentially. The lowest RMSE for the model is slightly greater than 5 when the regularization penalty is less than 1. When the regularization penalty increases to 10, the RMSE increases to almost 11. Since we originally chose 0.1 as our penalty parameter, we found one of the best performing models with the LASSO regression based on an RMSE value slightly greater than 5, which i comparable to the RMSE found in the first regression model with all 5 predictors. 
```{r}
#| message: false
#| label: figure13
#| fig-cap: "Figure 5: Parameter Tuning for LASSO Regression"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "final-figures", "lassoparameters.png"))
```

After creating the random forest model, we found that the RMSE and MAE values are exactly the same because the same 5 predictors are used for the outcome, but the R-squared value shows that the random forest model performs slightly better. Since a higher R-squared value represents smaller differences between the observed and predicted values, we can conclude that this model is predicting our outcome with slightly higher accuracy. The plot of the predicted versus observed values shown in @figure14 displays stronger correlation for predicted values compared to the testing and training done with cross-validation previously.  
```{r}
#| message: false
#| label: figure14
#| fig-cap: "Predicted vs Observed Values in Random Forest Model"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "final-figures", "randomforestpred.png"))
```

Again, it is crucial to tune hyperparameters associate with machine learning models. Based on the red line displayed in @figure15 that shows the lowest possible RMSE score, our random forest model performs the best with a node size of 1 and 4 predictors. This begs the question of which one of the 5 predictors included in our model should be dropped to improve model performance because all previous performance metrics suggested that including all 5 predictors created the best model. However, there is a minimal increase in RMSE when all five models are included in the model with a node size of 1.  
```{r}
#| message: false
#| label: figure15
#| fig-cap: "Tuning Parameters for Random Forest Model"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "final-figures", "randomforesttune.png"))
```

>>>>

We created a multitude of exploratory plots to understand our data better. The first exploratory result shown in @fig-1 displays the distribution of the outcome variable: percent of unintended pregnancies due to short acting reversible methods. The `pct_upreg_sarc` variable is slightly skewed to the right with an average around 12%.
```{r}
#| message: false
#| label: fig-1
#| fig-cap: "Number of Countries With Percent Unintended Pregnancy Using SARC"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "exploratory-figures", "pctupreg_sarc_distribution.png"))
```

The next set of variables we explored were the total counts of women using each birth control method. There were two large outliers that prevented the graphs from being useful. After exploring the outliers, we standardized using the population size of reproductive aged women (15-49 years). There is a positive association between the percentage of unintended pregnancies among short acting reversible method users and the total number of women using that method of birth control, which is to be expected. Our outcome variable is the number of unintended pregnancies among women who are using short-acting reversible contraception, so the number of unintended pregnancies that can be classified in this outcome is dependent on the number of women using this type of contraception. This percentage should increase as the number of women using short acting-reversible contraception increases because more women are at risk of experiencing an unintended pregnancy due to this contraception if they are using this type of contraception in the first place. This outcome variable does not speak to the effectiveness of short-acting reversible contraception, so it makes sense that our outcome would increase as more women put themselves at risk of experiencing the outcome through becoming classified as short-acting reversible contraception users. As explained in the supplementary material, the dataset includes the percentage of unintended pregnancies among long-acting reversible contraception and sterilization users, traditional birth control users, and users who do not use a method of birth control. Each of these percentages are positively associated with number of people in its respective classification group that it represents. The association for the contraception that we chose to focus on for this analysis, short acting reversible contraception, is displayed in @fig-2.
```{r}
#| message: false
#| label: fig-2
#| fig-cap: "Graph Depciting Percent Unintended Pregnancy by Standarized Count of Total Women"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "exploratory-figures", "pctupreg_totalsarc.png"))
```

We stratified these four graphs by region to examine how the relationship differs across each of the regions which is shown in @fig-3 . The graph for short acting reversible methods shows clearer differences between regions, and Latin America/the Caribbean leads in the percentage of unintended pregnancies in this category, but Africa shows the sharpest increase in percentage of unintended pregnancies as the total population increases.
```{r}
#| message: false
#| label: fig-3
#| fig-cap: "Graph Depicting Percent Unintended Pregnancies Using SARC by region"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "exploratory-figures", "pctupreg_sarc_stratified.png"))
```

We also created violin plots using the categorical usage variables for each birth control method as shown in @fig-4. It appears that the distribution of short acting reversible method usage is skewed towards lower percentages of unintended pregnancies across all usage levels, suggesting that more countries have lower percentage of unintended pregnancies among women using this method. The high usage countries appear to have a bottleneck in percentage of unintended pregnancies. The high and low usage countries appear to be skewed towards higher levels of unintended pregnancies, but the medium usage countries appear to have lower percentage of unintended pregnancies. 
```{r}
#| message: false
#| label: fig-4
#| fig-cap: "Violin Plot Depicitng Usage of SARc Per Region"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "exploratory-figures", "sarc_pctupreg_violin.png"))
```

Lastly, we explored the predictor variables that will be used in our models, and the graphs are shown in @fig-5 - @fig-10. The Africa region accounts for most of the observations with about 53 countries, followed by Asia that includes about 35 countries. Latin America/the Caribbean accounts for about 25 countries. Europe and Oceania account for the least number of observations. The distribution of women currently married is approximately normal with an average around 57% and no major outliers. The distribution of women never married is slightly skewed to the right with an average around 30%, but there are a few outliers greater than 60%. The distribution of the total maternal mortality rate is highly skewed to the right with a couple outliers. We would have expected the highest rates to belong to India and China because they have the most people, but it is Chad, Sierra Leone, and South Sudan that account for the highest rates of total maternal mortality, which each belong to the African region. The distribution of the maternal mortality rate from unintended pregnancies is highly skewed to the right with a couple outliers, which is to be expected based on the trend shown in the previous histogram. Chad and South Sudan also account for the highest rates of maternal mortality in this category. The distribution of maternal mortality rate from abortions is also highly skewed to the right. The outliers are accounted for by Gambia and Mauritania in this predictor, which both belong to the African region.
```{r}
#| message: false
#| label: fig-5 - fig 10
#| fig-cap: "Predictor Variable Distributions"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "exploratory-figures", "region_distribution.png"))
knitr::include_graphics(here("results", "figures", "exploratory-figures", "currmarried_distribution.png"))
knitr::include_graphics(here("results", "figures", "exploratory-figures", "nevmarried_distribution.png"))
knitr::include_graphics(here("results", "figures", "exploratory-figures", "matdeaths_distribution.png"))
knitr::include_graphics(here("results", "figures", "exploratory-figures", "matdeathsupreg_distribution.png"))
knitr::include_graphics(here("results", "figures", "exploratory-figures", "matdeathsabs_distribution.png"))

@@

## Basic statistical analysis
We completed a simple linear regression analysis with each of the 7 predictors shown in @tbl-2. The predictor with the strongest positive relationship with the outcome is total number of women using short acting reversible methods (`sarc_standard`). This percentage should increase as the number of women using short acting-reversible contraception increases because more women are at risk of experiencing an unintended pregnancy due to this contraception if they are using this type of contraception in the first place.

```{r}
#| message: false
#| label: tbl-2
#| fig-cap: "Strongest Predictor: sarc_standard"
#| echo: FALSE
readRDS(here("results","tables", "resulttable1.rds")) 
```

The second model we created used the region predictor, which revealed that the Latin America/the Caribbean region had the strongest relationship with the outcome variable followed closely by the Asia region. The Oceania region does not appear to have a strong effect on the outcome variable with the Europe region only showing a slightly larger association. These associations can be seen in @tbl-3.
```{r}
#| message: false
#| label: tbl-3
#| fig-cap: "Regional Predictor"
#| echo: FALSE
readRDS(here("results","tables", "resulttable2.rds")) 
```
Details about the 10 different models we created can be found in the statistical-analysis.qmd file in the code > analysis-code folder along with an exploration of the correlation between predictors.

@@

We created one model with all 5 predictors using multiple linear regression, shown in @tbl-4. This model shows the strongest predictor is the number of women using short acting reversible contraception. The next strongest predictor is the European region followed by the Latin America/the Caribbean region and the Asia region, which is a shift from the model with the singular region predictor. The Oceania region now has a negative association with the outcome. The currently married predictor is associated with a weak decrease in the outcome. The coefficient estimates for the rate of maternal death due to unintended pregnancies and abortion both show a very weak positive association with the outcome. 
```{r}
#| message: false
#| label: tbl-4
#| fig-cap: "Multiple Linear Regression with 5 Predictors"
#| echo: FALSE
readRDS(here("results","tables", "resulttable8.rds")) 
```
To determine which model performed the best, we started by examining the RMSE and MAE performance metrics. We found that the model with the standardized total count of women using the short acting reversible contraception method performed the best in a single predictor model compared to the percent of currently married women and the rate of maternal mortality due to abortion. @tbl-5 shows the RMSE and MAE values for each of these three models compared to the null model with no predictors. The model with the population size using SARCs is the only single predictor model that performs better than the null. The full model with all 5 predictors performs the best with the lowest RMSE and MAE values. 
```{r}
#| message: false
#| label: tbl-5
#| fig-cap: "Performance Metric Comparisons"
#| echo: FALSE
readRDS(here("results","tables", "resulttable14.rds")) 
```
We used cross-validation of the two best models to determine how well the model performs on data it has not seen yet by splitting the data into testing and training pieces. The cross-validated results, shown in @tbl-6 lead to the same conclusion: the multiple linear regression model with 5 predictors performs better. The RMSE value for the single predictor model with `sarc_standard` is 4.822226, which is lower the the first RMSE value of 5.143319. While the RMSE value for the multiple linear regression model is slightly higher than the first time it was calculated, it is still lower than the single predictor model. Additionally, the standard error of the RMSE for the multiple linear regression model is 0.2768, which is lower than the standard error of the RMSE for the single predictor model of 0.3528. This means there is higher variance in the single predictor model. The R-squared value of 0.8206 for the multiple linear regression model is higher than 0.7861 for the single predictor model, which means the multiple linear regression model accounts for more of the variability in the data. Overall, the multiple linear regression model performs better.
```{r}
#| message: false
#| label: tbl-6
#| fig-cap: "Cross Validation Performance Metric Comparisons"
#| echo: FALSE
readRDS(here("results","tables", "resulttable15.rds")) 
```

Since we determined that the full model with all 5 predictors performs best, we graphed the predicted versus observed values using this model with both the testing and training data to further examine model performance. As seen in @fig-11, the training model predictions, shown in teal, hover pretty closely around the expected relationship between the outcome and the 5 predictors, which is depicted as the 45 degree line. The testing model predictions, shown in coral, are much more extreme than the training model predictions because they are farther from the 45 degree line. While there is some overlap between the two sets of predictions, it is likely that our model is overfitting the data. 
```{r}
#| message: false
#| label: fig-11
#| fig-cap: "Evaluating Final Model Performance on Test Data"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "final-figures", "fullmodelpred.png"))
```
We went one step further to examine the uncertainty in the full model predictions using the bootstrap method with 100 resamples of the training data. The figure shown in @fig-12 displays the 95% confidence intervals, shown as dark blue lines, for the predictions made by the model. The confidence intervals are narrow, which shows there is minimal uncertainty in the model prediction. For the predictions that do not fall on the expected 45 degree line, the confidence intervals do not intersect with the line either. These findings increase the validity of the conclusion that the model is overfitting the data because there is not much uncertainty in the predictions. 
```{r}
#| message: false
#| label: fig-12
#| fig-cap: "Evaluation of Uncertainty in Full Model Predictions"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "final-figures", "bootstrappred.png"))
```

Since we have evidence that our model overfits the data, the last technique we want to use to explore our full model is Lasso regression. This technique could reveal predictors that should not be included in our final model, which could reduce the risk of overfitting. As seen in @tbl-7, the LASSO regression coefficients are much smaller than the first full model we created without the regularization penalty, but all 5 predictors remain in the model. The `sarc_standard` predictor still has the strongest relationship with the outcome. The percent of women currently married, rate of maternal deaths due to unintended pregnancies, and rate of maternal deaths to due to abortion all have weak negative associations with the outcome. This process confirms that our final model should contain all 5 predictors. 
```{r}
#| message: false
#| label: tbl-7
#| fig-cap: "LASSO Regression Results"
#| echo: FALSE
readRDS(here("results","tables", "resulttable16.rds")) 
```
It is important to tune the hyperparameters associated with LASSO regression to determine the model that fits best, which is shown in @fig-13. As the regularization penalty increases past 1, we see that the RMSE value increases exponentially. The lowest RMSE for the model is slightly greater than 5 when the regularization penalty is less than 1. When the regularization penalty increases to 10, the RMSE increases to almost 11. Since we originally chose 0.1 as our penalty parameter, we found one of the best performing models with the LASSO regression based on an RMSE value slightly greater than 5, which i comparable to the RMSE found in the first regression model with all 5 predictors. 
```{r}
#| message: false
#| label: fig-13
#| fig-cap: "Parameter Tuning for LASSO Regression"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "final-figures", "lassoparameters.png"))
```

After creating the random forest model, we found that the RMSE and MAE values are exactly the same because the same 5 predictors are used for the outcome, but the R-squared value shows that the random forest model performs slightly better. Since a higher R-squared value represents smaller differences between the observed and predicted values, we can conclude that this model is predicting our outcome with slightly higher accuracy. The plot of the predicted versus observed values shown in @fig-14 displays stronger correlation for predicted values compared to the testing and training done with cross-validation previously.  
```{r}
#| message: false
#| label: fig-14
#| fig-cap: "Predicted vs Observed Values in Random Forest Model"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "final-figures", "randomforestpred.png"))
```

Again, it is crucial to tune hyperparameters associate with machine learning models. Based on the red line displayed in @fig-15 that shows the lowest possible RMSE score, our random forest model performs the best with a node size of 1 and 4 predictors. This begs the question of which one of the 5 predictors included in our model should be dropped to improve model performance because all previous performance metrics suggested that including all 5 predictors created the best model. However, there is a minimal increase in RMSE when all five models are included in the model with a node size of 1.  
```{r}
#| message: false
#| label: fig-15
#| fig-cap: "Tuning Parameters for Random Forest Model"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "final-figures", "randomforesttune.png"))
```
